Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

..........(Describe why we use the rate of entrepreneurship indicators we chose)

@@

Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).  These three regression equations are as follows:

>>>>

@@

Starting with this explanatory variable, as mentioned earlier, we expected to observe different effects depending on the kind of entrepreneurship we looked at:

Therefore, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).  These three regression equations are as follows:
